Depression and suicidality as costly signals of need

### 2021-04-30 Paper.rmd
Small change in study aims and predictions

The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study. As the costs of a signal are expected to correspond to the reliability of the information provided, we predicted that costlier signals would (1) increase self-reported belief in the signaler's claims and (2) increase the likelihood of participants providing help, with (3) changes in likelihood of support being largely mediated by changes in the participants' belief in the signaler's need from pre-signal to post-signal.

>>>>

The primary aim of this study was to examine responses to various forms of emotional signaling in an experimental vignette study. As signals become less likely to be worth faking with increased costs, we predicted that costlier signals would (1) increase self-reported belief in the signaler's claims and (2) increase the likelihood of participants providing help, with (3) changes in likelihood of support being largely mediated by changes in the participants' belief in the signaler's need from pre-signal to post-signal.
